\section{Generation of referring expressions}\label{sec:gre}

In linguistics, a \emph{referring expression} (RE) is an expression that 
unequivocally identifies the intended target to the interlocutor, from a set of possible distractors.
%  
%For example, if we intend to identify a certain animal $d$ from a set of pets, the expression 
%``the dog'' will be an RE if $d$ is the only dog in the set, and if we are confident
%that our interlocutor will identify $d$ as a dog. 
%
The generation of referring expressions (GRE)  is a key task of most natural 
language generation (NLG) systems~\cite[Section 5.4]{dale2000}. 
Depending on the information available to the NLG system, certain objects might 
not be associated with an identifier which can be easily recognized by the user. 
In those cases, the system will have to generate a, possibly complex, description that contains 
enough information so that the interlocutor will be able to identify the intended referent.

The generation of referring expressions is a well developed field in automated natural language generation.
Building upon GRE foundational work~\cite{winograd,dale89cooking,Dale1995},
various proposals have investigated the generation of different kinds of referring expressions 
such as relational expressions (``the blue ball next to the cube''~\cite{dale91:_gener_refer_expres_invol_relat}),
reference to sets (``the two small cubes''~\cite{Stone2000}), or more expressive logical connectives (``the 
blue ball not on top of the cube''~\cite{deemter02:_gener_refer_expres}).
%
REs involving relations, in particular, have
received increasing attention recently.  However, the classical algorithm by~\shortcite{dale91:_gener_refer_expres_invol_relat} was shown to be unable to generate satisfying REs in practice (see the 
analysis over the \emph{cabinet corpus} in~\cite{viethen06:_algor_for_gener_refer_expres}).  Furthermore, the Dale
and Haddock algorithm and many of its successors (such as~\cite{kelleher06:_increm_gener_of_spatial_refer}) are vulnerable to
the problem of \emph{infinite regress}, where the algorithm enters an infinite loop, jumping back
and forth between descriptions for two related individuals, as in ``the book on the table which supports a book on the
table \ldots''

\shortcite{arec2:2008:Areces,arec:usin11} have proposed low complexity algorithms for the generation 
of relational REs 
%(including references to sets) 
that eliminate the risk of infinite regression. 
These algorithms are based on variations of the partition refinement algorithms of~\shortcite{paig:thre87}.
The information provided by a given scene is interpreted as a relational model whose 
objects are classified into sets that fit the same description.  
This classification is successively \emph{refined}  till the target 
is the only element fitting the description of its class.  The existence of an RE 
depends on the information available in the input scene, and on the expressive power of the formal 
language used to describe elements of the different classes in the refinement. 
%
%The idea of using a formal language to describe the information that an RE should convey has been discussed 
%already in~\cite{Krahmer2003,gardent07:_gener_bridg_defin_descr}.  In~\cite{arec2:2008:Areces,arec:usin11} the 
%combination of partition refinement algorithms and different formal languages is used to classify existing 
%GRE approaches in an expressiveness hierarchy.  For instance, the classical Dale and Reiter algorithms
%compute purely conjunctive formulas; \cite{deemter02:_gener_refer_expres} extends this language by
%adding the other propositional connectives, whereas~\cite{dale91:_gener_refer_expres_invol_relat} extends it by
%allowing existential quantification.
%
Refinement algorithms %presented in~\cite{arec2:2008:Areces,arec:usin11} 
effectively compute REs for all individuals in the domain, at the same time. The algorithms always terminate returning a formula of 
the formal language chosen that uniquely describes the target (if the 
formal language is expressive enough to identify the target in the input model). 
%\shortcite{arec2:2008:Areces}
%show that the refinement algorithm using the description language \el  is capable of generating 67\% of 
%the relational REs in the~\cite{viethen06:_algor_for_gener_refer_expres} dataset, when all possible orders of the relations in the domain are considered. This is in sharp contrast with the analysis 
%done in~\cite{viethen06:_algor_for_gener_refer_expres} over the cabinet corpus, of algorithms based in Dale and Reiter's original proposal.    
%
Refinement algorithms require an 
ordered list of properties that can be used to described the objects in the scene, and the naturalness of the generated REs strongly depends on this ordering. 
%coverage results reported over Viethen and 
%Dale's cabinet corpus means that \emph{some ordering} produces a reasonably wide coverage.  In other words, it has been shown that refinement algorithms have the capacity of producing REs similar to those produced by human subjects, provided a suitable ordering over relations appearing 
%in the input scene is available, but it is unclear which of all possible orders should be used.  In this article we directly address this issue.  
The goal of this paper is twofold. First we show how we can add non-determinism and overspecification to the refinement algorithms, by replacing the fixed ordering 
over properties of the input scene by a \emph{probability of use} for each property, and modifying the algorithm accordingly.  
In this way, each call to the algorithm can produce different REs for the same input scene and target.  We will then show that given suitable corpora of REs (like the GRE3D7 corpora discussed in~\cite{viet:gene11}) we can estimate these probabilities of use so that REs are generated with a probability distribution that matches the one found in corpora.  

%The rest of the paper is structured as follows. In Section~\ref{sec:algorithm} we introduce the technical details of the 
%refinement algorithms presented in~\cite{arec2:2008:Areces,arec:usin11} and show how to introduce non-determinism using 
%the probability of use of properties in the input scene.  In this section, we assume that these probabilities are provided as 
%input to the algorithm. In Section~\ref{sec:learning}, we show how to estimate the 
%probability of use of a property from training data. Given corpora consisting of pairs (scene, target) together with the REs used to 
%describe the target in each case, we propose a method to compute the probability of use of each property for each scene, and use a machine learning approach to generalize these properties to new targets and scenes not appearing in the training set. 

%Testing of the resulting algorithms shows that there is still one factor missing to properly account for the REs found in corpora: overspecification.  Refinement algorithms only allow a mild form of overspecification in the REs produced.  We discuss this in Section~\ref{sec:overspecification} and propose a modification that let the algorithm generate overspecified, but non trivially redundant RE.  The modification proposed is inspired by the work of~\shortcite{keysar:Curr98} on the egocentric basis of language.  
%Section~\ref{sec:evaluation} presents a quantitative evaluation of the resulting algorithm. We show that when trained with scenes from the GRE3D7 corpora the algorithm can generate REs with a probability distribution that, in certain scenes, coincides with an up to 84.49\% of accuracy with the probability distribution of REs used by humans for that scene. 

%In Section~\ref{sec:discussion} we discuss related work, motivations and future lines of research, focusing on the role of non-determinism and overspecification in the generation of referring expressions. 

