
%%%%%%%%%%%%%%%%%%%%%  -*- mode: LaTeX; coding: koi8-r; -*-
%%%  Altamirano Ivana Romina   %%%
%%%%%%%%%%%%%%%%%%%%%
%%
%%  Date: 2008
%%  Author: IRA (romina.altamirano@gmail.com)
%
%\documentclass[oneside]{book} 
\documentclass[a4paper,12pt]{article}
\hyphenation{mo-de-lo re-fe-ren-cial a-pro-xi-ma-cio-nes re-a-li-za-das ma-nual-men-te par-ti-cu-lar ma-yo-ri-ta-ria-men-te ma-ne-ra re-le-va-mien-to}
\usepackage{natbib}\setlength{\bibsep}{5pt}
\bibpunct{[}{]}{;}{a}{,}

\usepackage{colortbl}

%\usepackage{tocbibind}
%\usepackage[T2A]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[spanish]{babel}
%\usepackage[dvips]{graphicx}
\usepackage{a4wide}
%\usepackage{chicago}
\usepackage{hyperref}

\begin{document}
\renewcommand{\refname}{Bibliograf\'ia}
%\begin{titlepage}

\begin{center}


\vspace{5cm}
{\Large Proyecto y Plan de Trabajo Doctoral}\\[0.5cm]

\vspace{2cm}

% Title
%\HRule \\[0.4cm]
{ \Large \bfseries Generaci\'on de expresiones referenciales y aplicaciones} \\ 

\vspace{0.5cm}


% Author and supervisor
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Alumna:}\\
Ivana Romina \textsc{Altamirano}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisora:} \\
Dra.~Luciana \textsc{Benotti}
\end{flushright}
\end{minipage}

\vspace{2cm}

% Bottom of the page
{\large FaMAF, \today}

\end{center}

%\end{titlepage}

%\maketitle
%\date{}
%\tableofcontents{}
%\newpage


\input{intro}
\input{objetivos}
\input{plandetrabajo}
%\input{progreso}

\addcontentsline{toc}{section}{Bibliograf\'{\i}a}
%\bibliographystyle{plain}
%\bibliography{bibliografia}
%\printgloss{glsbase,glosario}

\begin{thebibliography}{10} \renewcommand{\itemsep}{-2pt}

\bibitem{arec:2012:coling12}
Romina Altamirano, Carlos Areces, and Luciana Benotti.
\newblock Probabilistic refinement algorithms for the generation of referring
  expressions.
\newblock In {\em Proceedings of the 24th International Conference on
  Computational Linguistics}, pages 53--62, 2012.

\bibitem{benotti-altamirano-jair}
Romina Altamirano, Carlos Areces, and Luciana Benotti.
\newblock Probabilistic refinement algorithms for the generation of referring
  expressions.
\newblock {\em Journal of Artificial Intelligence Research {(JAIR)}, Artificial
  Intelligence}, (to be submitted).

\bibitem{Areces2008}
Carlos Areces, Alexander Koller, and Kristina Striegnitz.
\newblock {Referring expressions as formulas of description logic}.
\newblock In {\em Proceedings of the Fifth International Natural Language
  Generation Conference on - INLG '08}, pages 42--49, Morristown, NJ, USA,
  2008. Association for Computational Linguistics.

\bibitem{benotti-altamirano-context2013}
Luciana Benotti and Romina Altamirano.
\newblock Evaluation of a refinement algorithm for the generation of referring
  expressions.
\newblock In Patrick Br\'ezillon, Patrick Blackburn, and Richard Dapoigny,
  editors, {\em Modeling and Using Context}, volume 8175 of {\em Lecture Notes
  in Computer Science}, pages 31--44. Springer Berlin Heidelberg, 2013.

\bibitem{Callaway2005}
Charles Callaway, Elena Not, Alessandra Novello, Cesare Rocchi, Oliviero Stock,
  and Massimo Zancanaro.
\newblock {Automatic cinematography and multilingual NLG for generating video
  documentaries}.
\newblock {\em Artificial Intelligence}, 165(1):57--89, June 2005.

\bibitem{Cox1999}
Richard Cox, Mick O'Donnell, and Jon Oberlander.
\newblock {Dynamic versus static hypermedia in museum education: an evaluation
  of ILEX, the intelligent labelling explorer}.
\newblock In {\em Proceedings of the Artificial Intelligence in Education
  conference}, pages 181--188. Citeseer, 1999.

\bibitem{Dale2009}
Robert Dale and Jette Viethen.
\newblock {Referring expression generation through attribute-based heuristics}.
\newblock {\em Proceedings of the 12th European Workshop on Natural Language
  Generation - ENLG '09}, (March):58--65, 2009.

\bibitem{DaleRobertandHaddock1991}
Nicholas {Dale, Robert and Haddock}.
\newblock {Generation of Referring Expressions Involving Relations}.
\newblock In {\em EACL '91 Proceedings of the fifth conference on European
  chapter of the Association for Computational Linguistics}, October 1991.

\bibitem{delucenaENLG}
Diego~Jesus de~Lucena and Ivandr{\'e} Paraboni.
\newblock {USP-EACH}: Improved frequency-based greedy attribute selection.
\newblock In {\em Proceedings of the 12th European Workshop on Natural Language
  Generation (ENLG 2009)}, pages 189--190, Athens, Greece, March 2009.
  Association for Computational Linguistics.

\bibitem{gattENLG}
Albert Gatt, Anja Belz, and Eric Kow.
\newblock The tuna challenge 2008: Overview and evaluation results.
\newblock In {\em Proceedings of the 5th International Conference on Natural
  Language Generation (INLG 2008)}, pages 198--206. Association for
  Computational Linguistics, 2008.

\bibitem{keysar:Curr98}
Boaz Keysar, Dale~J. Barr, and William~S. Horton.
\newblock {The Egocentric Basis of Language Use}.
\newblock {\em Current Directions in Psychological Science}, 7(2):46--49, April
  1998.

\bibitem{KrahmerEmielandVanDeemter2011}
Emiel Krahmer and Kees~Van Deemter.
\newblock {Computational Generation of Referring Expressions: A Survey}.
\newblock {\em Computational Linguistics}, 2011.

\bibitem{Krahmer2003}
Emiel Krahmer, Sebastiaan~Van Erk, and Andr\'{e} Verleg.
\newblock {Graph-Based Generation of Referring Expressions}.
\newblock {\em Computational Linguistics}, 29(1):53--72, March 2003.

\bibitem{Mellish2006}
Chris Mellish, Donia Scott, Lynne Cahill, Daniel Paiva, Roger Evans, and Mike
  Reape.
\newblock {A Reference Architecture for Natural Language Generation Systems}.
\newblock {\em Natural Language Engineering}, 12(01):1, March 2006.

\bibitem{Reiter2000}
E.~Reiter and R.~Dale.
\newblock {\em {Building natural language generation systems}}.
\newblock Cambridge University Press, 2000.

\bibitem{Reiter09}
Ehud Reiter and Anja Belz.
\newblock {An Investigation into the Validity of Some Metrics for Automatically
  Evaluating Natural Language Generation Systems}.
\newblock {\em Computational Linguistics}, (December 2008), 2009.

\bibitem{ruudINLG2012}
Koolen Ruud, Krahmer Emiel, and Theune Mari\"{e}t.
\newblock Learning preferences for referring expression generation: Effects of
  domain, language and algorithm.
\newblock In {\em INLG 2012 Proceedings of the Seventh International Natural
  Language Generation Conference}, pages 3--11, Utica, IL, May 2012.
  Association for Computational Linguistics.

\bibitem{viethen-dale:2011:UCNLG+Eval}
Jette Viethen and Robert Dale.
\newblock Gre3d7: A corpus of distinguishing descriptions for objects in visual
  scenes.
\newblock In {\em Proceedings of the UCNLG+Eval: Language Generation and
  Evaluation Workshop}, pages 12--22, Edinburgh, Scotland, July 2011.
  Association for Computational Linguistics.

\end{thebibliography}



%\bibitem{Hutchins2006} [Ref Hutchins http://www.hutchinsweb.me.uk/CUHK-2006.pdf]

\end{document}
